---
title: "rembgR Vignette"
author: "Gabe Runte"
date: "2023-11-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(jpeg) #image processing
library(raster) #image processing
library(sf) #image processing
library(doParallel) #Paralleliz
source(here("functions.R"))
```

This project came about as a result of my need to isolate photos of plants from their backgrounds. We took photos of seedlings using a R,G,NIR camera for the purposes of calculating NDVI over time. This made sense because it is difficult to use common plant physiology tools to measure performance of small needle-leaved seedlings (this was prior to the recent LiCor needle attachment!). 
We attempted to use thresholds in reflectance to isolate plants from their environment but results were mixed. So below is a prief workflow showing the utility of this toolkit for isolating plants and visualizing NDVI in a greenhouse context! Niche, I know. 
```{r}
#Following the same steps as in the rembgR_demo.Rmd file
directory = here("vignette", "seedling_photos")
folder_in = "raw"
folder_out = "raw_trimmed"
rembg(photo_directory = directory, input_path = folder_in, output_path = folder_out)
```

Now, I go through and pull back in each of the images and plot their NDVI values before and after background removal to show the utility! 
```{r}
#First, I need to list all of the photos
raw_photos = list.files(paste(directory, folder_in, sep = "/"))
trimmed_photos = list.files(paste(directory, folder_out, sep = "/"))

#Next I make a dataframe of the photos, their file paths, and which group they belong to
all_photos = tibble(photo = raw_photos) %>% 
  mutate(path = paste(paste(directory, folder_in, sep = "/"), photo, sep = "/")) %>%
  mutate(class = "raw") %>% 
  bind_rows(tibble(photo = trimmed_photos) %>% 
  mutate(path = paste(paste(directory, folder_out, sep = "/"), photo, sep = "/")) %>% 
    mutate(class = "trimmed")
  )

#Finally, I run a for() loop that loads the image, calculates the NDVI, and plots the output. We should see two plots for each seedling, one untrimmed and one trimmed. 
for(i in 1:length(all_photos$photo)){

aq = stack(all_photos$path[i])
bq = brick(aq)
ndvi <- (bq[[3]] - bq[[1]]) / (bq[[3]] + bq[[1]])

min_color_ndvi <- -.25
max_color_ndvi <- .25

# Create a color palette
color_ndvi <- colorRampPalette(c("orange", "darkgreen"))(256)

plot(ndvi, col = color_ndvi, breaks = seq(min_color_ndvi, max_color_ndvi, length.out = length(color_ndvi)), axes = FALSE, xlim = c(0,4000), legend=FALSE)}


```

